MSE and dynamic state variable model with sigma function

### 2017-12-20 doc/previous versions/MSE_OCT.tex
changes scenarios MP

@@

\subsubsection{Size dependant pricing}
\label{sec2.2.1}
% Prices of fish have been assumed to be constant over fish age and time.
Common knowledge and case studies indicated that size and weight of a fish could be important attributes when determining its economic value. However, so far there has been no broader assessment whether the size-dependence of price really is prevalent and significant in fisheries. The results from \cite{Zimmermann2011, Zimmermann2013} underline that size-dependent pricing is common in Norwegian fisheries, and is therefore also of high relevance for decisions in fisheries management. Therefore, the resulting data of mean weights, average prices and total yield per weight classes and year were used for further analysis. We fitted linear mixed models (Bates and Maechler, 2010) and general additive models (Wood, 2010) in R (R: Development Core Team, 2012), using mean price and mean body weight as the response variable and covariate, respectively. Thus, the statistical models took the form  
\begin{equation}
 p_{i} \sim c_{0} + c_{1} w_{i} + f (y_{i}), 
\end{equation}
where p is price of observation i, wi is the mean weight of the corresponding weight class, and the term f(yi) corresponds to the effect of year, treated either as a random effect or as a smooth term. Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Size dependant pricing.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}lcccccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{6}{c}{season} \\ 
age                      & 1     & 2     & 3    & 4    & 5    & 6    \\ \hline
                      \\
1                       &    &    &   &   & & \\
2                       &    &    &   &   & &\\
3                       &    &    &   &   & &\\
4                       &    &    &   &   & &\\
\\
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l c c  c }
\hline
                                & \textbf{Scenario I}            & \textbf{Scenario II}                 & \textbf{Scenario III}           \\ 
                                & \textit{(landings selectivity)}  & \textit{(fulll avoidance of discards)} & \textit{(LO not fully enforced)} \\ \hline
& & &  \\
Discarding                      & Allowed                        & Not allowed                          & Ocurred but not perceived \\
Manager catch perception        & $C = L + D$                    &        $C = L$                       &  $C = L$  \\
Yield per recruitment model     & based in $F_L$                 &       based in $F_C$                 &  based in $F_L$  \\
Selectivity ($L/C$)             &  $ \neq 1$                     & $=1$                                 & $=1$\\
&  & &  \\\hline
\end{tabular}
}
\end{table}

@@

\begin{equation}
 Q_{MSY} = \frac
                % Nominator
                {\sum( [\frac{H_{MSY}}{\bar{H}} \times H (a, s) \times lratio (a, s) \times B numbers(a, s)] \times wts) }
                % Denominator
                {number of vessels}, 
\end{equation}
\begin{equation}
 Q (y+1) = \max( \min(Q_{MSY}, Q(y) \times 1.15), Q(y) \times 0.85)), 
\end{equation}

>>>>

\begin{figure}[!h]
\centering
\begin{minipage}{.4\textwidth}
\includegraphics[width=\textwidth]{Figures/Areadynamics.eps} 
\end{minipage}
\hfill
\begin{minipage}{.5\textwidth}
\includegraphics[width=\textwidth]{Figures/MSE.eps} 
\end{minipage}
\caption{The conceptual framework and how it was mapped.}
\end{figure}

@@

\subsubsection{Size dependant pricing}
\label{sec2.2.1}
Prices of fish have been assumed to be fixed over time but influenced by the size of the catch. Common knowledge and case studies indicated that size and weight of a fish could be important attributes when determining its economic value \cite{Zimmermann2011, Zimmermann2013}. Therefore, the resulting data of mean weights and average prices were used for further analysis. We fitted linear mixed models, using mean price and mean body weight as the response variable and covariate, respectively. Thus, following \cite{Zimmermann2011}, the statistical models took the form:  
\begin{equation}
 pw_{i} \sim p_i \bar{w_i} + \beta_0 \times \frac{w_i-\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p$ is the mean price of species $i$, $\bar{w_i}$ is the mean weight of the corresponding weight classes, and the fraction corresponded to the standarization of the mass relative to the mean observed individual catch mass over all ages classes. $\beta_0$ gave the price increase when individial mass was increased by $\bar{w}$.
 %Because landings corresponding to each weight class varied dramatically, sometimes by several orders of magnitude, we used log-transformed total annual yield per weight class as the statistical weighting factor in the above models. Alternatively, to test the sensitivity of the results, we did not apply any weighting but excluded data corresponding to the lowest 10\% quantile of annual yield, so that observations corresponding to very low yields would not influence the results. All models were fitted independently to each stock.
\begin{table}[!h]
\centering
\caption{Size dependant pricing.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}lcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
                         & 1     & 2     & 3    & 4   \\ \hline
                      \\
species 1                &  778  & 1354   & 1780  & 2096  \\
species 2                &  778  & 1354   & 1780  & 2096  \\
\\
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l c c  c }
\hline
                                & \textbf{Scenario I}            & \textbf{Scenario II}                 & \textbf{Scenario III}           \\ 
                                & \textit{(landings selectivity)}& \textit{(fulll avoidance of discards)} & \textit{(LO not fully enforced)} \\ \hline
& & &  \\
Discarding                      & Allowed                        & Not allowed                          & Ocurred but not perceived \\
Manager catch perception        & $C = L + D$                    &        $C = L$                       &  $C = L$  \\
Yield per recruitment model     & based in $F_L$                 &       based in $F_C$                 &  based in $F_L$  \\
Selectivity ($L/C$)             &  $ \neq 1$                     & $=1$                                 & $=1$\\
&  & &  \\\hline
\end{tabular}
}
\end{table}

@@

\begin{equation}
 Q_{MSY} = \frac
                % Nominator
                {\sum( [\frac{H_{MSY}}{\bar{H}} \times H (a, s) \times lratio (a, s) \times B numbers(a, s)] \times wts) }
                % Denominator
                {number of vessels}, 
\end{equation}
\begin{equation}
 Q (y+1) = \max( \min(Q_{MSY}, Q(y) \times 1.15), Q(y) \times 0.85), 
\end{equation}
